Dynastic Extinctions and Urban Economic Development: \\Evidence from the Holy Roman Empire\footnote{I thank Davide Cantoni, Matthias Weigand, and my RA colleagues at the Chair of Economic History for helpful comments and feedback.}

### 2023-06-22 paper/paper.tex
#28 add first results paragraph

\section{Data}

@@

The basic assumption that needs to be satisfied for a causal interpretation of TWFE estimates is parallel trends. This means that, absent treatment, the outcome in cities that received treatment would have followed the same time trend as the outcome in never-treated cities. While it is impossible to empirically prove this assumption (because we cannot observe the counterfactual trend), it is common to check its validity by estimating pre-treatment effects: if the treatment and control group already showed different trends before being treated, there may be an unobserved variable correlated both with receiving treatment and with the outcome, biasing the estimate. For this reason I also include leads reaching 100 years into the past in my regression (as do \cite{schoenholzer2022}.)

@@

Table \ref{tab:SW22_replication_50y} shows estimates for Equation \eqref{eq:sw22}. Figure \ref{fig:SW_replication} plots the coefficients in column (1) to visualise how the effect evolves dynamically.

The

>>>>

\section{Data} \label{sec:data}

@@

The basic assumption that needs to be satisfied for a causal interpretation of TWFE estimates is parallel trends. This means that, absent treatment, the outcome in cities that received treatment would have followed the same time trend as the outcome in never-treated cities. While it is impossible to empirically prove this assumption (because we cannot observe the counterfactual trend), it is common to check its validity by estimating pre-treatment effects: if the treatment and control group already showed different trends before being treated, there may be an unobserved variable correlated both with receiving treatment and with the outcome, biasing the estimate. For this reason I include a lead reaching 100 years into the past in my regression (as do \cite{schoenholzer2022}.)

@@

Table \ref{tab:SW22_replication_50y} contains estimates from Equation \eqref{eq:sw22}. Each column reports the effect of switching states on a different subset of observed construction activity: Column (1) for all types of buildings, Column (2) for administrative, military and representative buildings, Column (3) for private construction, and Column (4) for buildings that provide public goods. The exact definitions of these categories are as described in Section \ref{sec:data}.

We can see in Column (1) that switching states has no immediate effect (relative to the period that precedes the switch) on the probability of recorded construction activity; over the following 200 years, however, the effect grows positive and significant.

Figure \ref{fig:SW_replication} plots the coefficients in Column (1) to visualise how the effect evolves dynamically.
